### 2015-05-15 evaluation.tex

Most of the races that \whoop and \corral discovered can be classified in two cases. The first case is accessing a global counter (or flag) from concurrent entry points, without a lock. This might be for performance, and indeed a lot of the races we found might be benign. Even benign races, though, lead to undefined behavior according to the C standard, and it is well known that undefined behaviors can lead to unexpected results when combined with aggressive compiler optimizations. The second case is an entry point accessing a field of an object (either global or passed as a parameter) without a lock. This can lead to a race if another entry point simultaneously accesses the same field of the same object.

>>>>

Most of the races that \whoop and \corral discovered can be classified in two cases. The first case is accessing a global counter (or flag) from concurrent entry points, without a lock. This might be for performance, and indeed a lot of the races we found might be benign. Even benign races, though, lead to undefined behavior according to the C standard, and it is well known that undefined behaviors can lead to unexpected results when combined with aggressive compiler optimizations. The second case is an entry point modifying a field of a struct (either global or passed as a parameter) without a lock. This can lead to a race if another entry point simultaneously accesses the same field of the same struct.

### 2015-05-15 related.tex

Prior works on static race checking include: \cite{choi2002efficient}, which combines static analysis, optimized instrumentation and runtime access caching to speedup dynamic data race detection; \cite{kahlon2007fast}, which combines a divide-and-conquer strategy that partitions all pointers of a program that cannot alias in disjoint sets and function summarization to achieve a scalable context-sensitive alias analysis for data races; \cite{kahlon2009semantic}, which uses abstract interpretation to achieve a sound partial-order reduction on the set of thread interleavings and statically reduce the number of false data race warnings; and \cite{das2015section}, which combines inter-procedural pointer analysis with verifiable user annotations to split programs into disjoint sections, based on non-communicating accesses of shared data, and eliminate redundant checks during dynamic race detection.

>>>>

Prior works on static race checking include: \cite{choi2002efficient}, which combines static analysis and runtime access caching to speedup dynamic race detection; \cite{kahlon2007fast}, which uses a divide-and-conquer algorithm that partitions all pointers of a program that do not alias in disjoint sets to achieve a scalable race analysis; \cite{kahlon2009semantic}, which uses abstract interpretation to achieve a sound partial-order reduction on the set of thread interleavings and statically reduce the number of false race warnings; and \cite{das2015section}, which employs inter-procedural alias analysis and verifiable user annotations to split programs into disjoint sections, based on non-communicating accesses of shared data, and eliminate redundant checks during dynamic race detection.

### 2015-05-15 whoop.tex

Symbolic verification of a pair of entry points works by (i) instrumenting each entry point with additional state to record locksets, and (ii) attempting to verify a sequential program that executes the instrumented entry points in sequence and then asserts, for each shared location, that the locksets for each entry point with respect to this location have a non-empty intersection.  Verification of the resulting sequential program can be undertaken using any sound method; in practice we employ the Boogie verification engine~\cite{barnett2006boogie}, which requires procedure specifications and loop invariants to be generated, after which verification conditions~\cite{barnett2005weakest} (VCs) are generated and discharged to an automated theorem prover.

>>>>

Symbolic verification of a pair of entry points works by (i) instrumenting each entry point with additional state to record locksets, and (ii) attempting to verify a sequential program that executes the instrumented entry points in sequence and then asserts, for each shared location, that the locksets for each entry point with respect to this location have a non-empty intersection.  Verification of the resulting sequential program can be undertaken using any sound method; in practice we employ the Boogie verification engine~\cite{barnett2006boogie}, which requires procedure specifications and loop invariants to be generated, after which verification conditions~\cite{barnett2005weakest} (VCs) are generated and discharged by an automated theorem prover.
